\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
A nice white sauce for the pasta

To grant a user an identity on a realm, the user first presents a username and
password to the server, after which the server delegates authority for that
name to the client by signing that client's key. This key-signing process is
the method by which peers can authenticate securely to each other without a
centralized broker.

>>>>

Each \Trill domain should host a federation server, which is able to delegate
authority for identities to various clients.  Any client may present the server
with an identity and a password for that identity.  If the client's
authentication succeeds, the server signs the client's key and returns the
resultant certificate.  Using these certificates, clients can then authenticate
securely to one another without further use of the server.
